---
title: "Assignment 4 - Spiny Lobsters"
author: "Vanessa Rathbone and Nicole Schmidt"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Attach library packages
# Read in data and tidy it

library(tidyverse)
library(purrr)
library(ggplot2)
library(janitor)

# Read in data with clean_names()

lobster_tidy <- readr::read_csv("lobster_abundance_sbc_lter.csv",
na = "-99999") %>% 
  clean_names()

# Results A: Visually explore changes in annual lobster abundance (counts) by site.

lobster_ysite_a <- lobster_tidy %>% 
  count(year, site) %>% 
  mutate("MPA" = ifelse(site == "IVEE", "MPA",
                        ifelse(site == "NAPL", "MPA",
                               "non-MPA"))) %>% 
  mutate("site_name" = ifelse(site == "IVEE", "Isla Vista",
                              ifelse(site == "NAPL", "Naples",
                                     ifelse(site == "AQUE", "Arroyo Quemado",
                                            ifelse(site == "CARP", "Carpenteria",
                                            "Mohawk")))))

# Results B: Visually explore lobster size distribution shifts by comparing lobster sizes in 2012 and 2018

lobster_size_site_b <- lobster_tidy %>%
  filter(year %in% c(2012, 2018))
  
# need to find standard diviation of lobster size distribution 
# because it's a distribution plot we may want to consider a density or histogram plot
  

```

##### INTRO (both)
# need to rewrite
# add image of a spiny lobster and the map of the locations? if so, add references to bottom

Abstract:	
Data on abundance, size and fishing pressure of California spiny lobster (Panulirus interruptus) are collected along the mainland coast of the Santa Barbara Channel. Spiny lobsters are an important predator in giant kelp forests off southern California. Two SBC LTER study reefs are located in or near the California Fish and Game Network of Marine Protected Areas (MPA), Naples and Isla Vista, both established as MPAs on 2012-01-01. MPAs provide a unique opportunity to investigate the effects of fishing on kelp forest community dynamics. Sampling began in 2012 and is ongoing.

This dataset contains two tables. 1) Abundance and size data collected annually by divers in late summer before the start of the fishing season at five SBC LTER long term kelp forest study sites: two within MPAs (Naples and Isla Vista) and three outside (Arroyo Quemado, Mohawk and Carpinteria). 2) Fishing pressure, as determined by counting the number of commercial trap floats. Data are collected every two to four weeks during the lobster fishing season (October to March) at nine sites along the mainland, eight of which are also SBC LTER long-term kelp forest study reefs.

##### DATA AND METHODS (both)
```{r}

```

###### RESULTS A Abundance of lobsters per site
```{r}

# Exlore data viz for lobster count per site per year

ggplot(data = lobster_ysite_a, aes(x = year,
                                   y = n)) +
  geom_line(aes(color = site)) +
  
            
            
# scale_color_manual(breaks = c("MPA", "non-MPA"), values = c("blue", "orange")


```

###### RESULTS B size dif per site
```{r}

lobster_size_2012 <- lobster_tidy %>%
  filter(year == 2012) %>% 
  group_by(site) %>%
  summarize(total = mean(size_mm, na.rm = TRUE)) %>% 
  mutate(year = 2012)

lobster_size_2018<- lobster_tidy %>% 
  filter(year == 2018) %>% 
  group_by(site) %>%
  summarise(size_avg = mean(size_mm, na.rm = TRUE)) %>%
  mutate(year = 2018)

```

###### RESULTS C means per MPAs
```{r}

```

##### SUMMARY 
```{r}

```

##### REFERENCES

Reed D. 2019. SBC LTER: Reef: Abundance, size and fishing effort for California Spiny Lobster (Panulirus interruptus), ongoing since 2012. Environmental Data Initiative. https://doi.org/10.6073/pasta/a593a675d644fdefb736750b291579a0. Dataset accessed 10/30/2019.

